\documentclass{article}
\usepackage{verse}
\usepackage[usenames, dvipsnames]{color}

\newcommand{\attrib}[1]{%
\nopagebreak{\raggedleft\footnotesize #1\par}}
\renewcommand{\poemtitlefont}{\normalfont\large\itshape\centering}

\begin{document}

\poemtitle{One Another}
\settowidth{\versewidth}{Than Tycho Brahe, or Erra Pater:}
\begin{verse}[\versewidth]
I am one            \\
But one,            \\
Of another          \\
I am glad           \\
That there's not    \\
Only one,           \\
But another.        \\
I can be lonely     \\
I can be alone      \\
I can writhe        \\
In the worst of what exists \\
But, I am glad;     \\
I'm one             \\
Of another          \\
\end{verse}

\poemtitle{Subtle}
\settowidth{\versewidth}{Than Tycho Brahe, or Erra Pater:}
\begin{verse}[\versewidth]
Subtle in the way that it talks \\
Quiet \\
Down, listen to others speak \\
Not other yous but other theys \\
Theys in a good way \\ 
If there are good ways \\
To other \\
Utter \\
In subtle ways \\
\end{verse}


\poemtitle{Cheater}
\settowidth{\versewidth}{Than Tycho Brahe, or Erra Pater:}
\begin{verse}[\versewidth]
I’m a cheater and her name is heather \\
You could smell her on me \\
Most days \\
Like a spring meadow \\
Pure \\
Like a virgin \\
Except Madonna prays \\
Pure
Like a version \\
Between the sheets \\
Dryer \\
\end{verse}

\newpage

\poemtitle{Cheater 2}
\settowidth{\versewidth}{Than Tycho Brahe, or Erra Pater:}
\begin{verse}[\versewidth]
I’m a cheater and her name is heather \\
She hangs on my neck \\
Crucial, \\
Crew, sure. \\
Other people call her by her other name, \\
Grey... \\
To them she's plain \\
Mundane \\
Even, \\
But you should see her in the evening. \\
Warm \\
Soft \\
Her name is Heather Grey. \\
Her name is Heather Grey. \\
Her name is Heather Grey. \\
\end{verse}

\poemtitle{Cinderella}
\settowidth{\versewidth}{Than Tycho Brahe, or Erra Pater:}
\begin{verse}[\versewidth]
Your eyes \\
When you said goodbye \\
Ugh \\
You did say, \\
Good-Bye. \\
I wonder when you pierced your nose \\
Are you done with this? \\
Yeah. \\
Do you always smile like this? \\
I was just trying to eat some vegetables \\
This week. \\
Right? \\
Do you always smile like this? \\
I wonder when she pierced her nose. \\
Yeah, I try to eat healthy too, \\
Never works out. \\
\\
Yeah. \\
\end{verse}

\newpage

\poemtitle{Hallways}
\settowidth{\versewidth}{Than Tycho Brahe, or Erra Pater:}
\begin{verse}[\versewidth]
Walking through the \\
Hall \\
Looking for an open door, \\
No luck. \\
I open the door, and\\
There\\
You\\
Were\\
I hold the door\\
––I hold my breath––\\
But don't take a second\\
Look\\
Who are you?\\
Never seen you before\\
Most beautiful soul I've seen\\
All year\\
This place is so big\\
I might not see you again\\
Farewell\\
May we never meet again\\
I'd still lack the courage\\
To speak. ``Thank you''.\\

You're welcome.\\
\end{verse}

\newpage

\poemtitle{Immortal}
\settowidth{\versewidth}{Than Tycho Brahe, or Erra Pater:}
\begin{verse}[\versewidth]
Today, \\
I fell in love; \\
For the thousandth time. \\
It's you \\
That noticed my heart \\
A thousandth time. \\
It's like you've granted \\
Me, \\
A thousandth year, \\
In this moment, \\
I've lived, \\
In my, imagination, with \\
You \\
We've grown old \\
and neither of \\
Us, \\
Have noticed as \\
We, \\
Pass each other on the street. \\
\end{verse}



\poemtitle{Mere Mortal}
\settowidth{\versewidth}{Than Tycho Brahe, or Erra Pater:}
\begin{verse}[\versewidth]
I think, \\
Sometimes I think,\\
It's right that \\
I \\
Am but a mere mortal. \\
Let my good ideas \\
Live on in someone else \\
Let my bad ideas \\
Lie with me. \\
Lie with me, \\
Inanimate- \\
Ly. Buried.
Forgotten, but necessary \\
Like sand \\
In concrete \\
I don't pray. \\
But when I do, \\
I pray the gods\\
Let me be, \\
But a mere mortal \\
And let me leave. \\
\end{verse}


\poemtitle{Ignorance Divine}
\settowidth{\versewidth}{Than Tycho Brahe, or Erra Pater:}
\begin{verse}[\versewidth]
Answers. \\
Objective answers exists \\
& \\
I'm here to find them. \\
Like a switch in the dark,\\
Which flip is on? \\
Does it matter–– \\
Asker, \\
Hear me; Behold! \\
I Am the Asker \\
And the Answerer. \\
The Beginning and The End. \\
The Truth, \\
And The Lie. \\
Ask, and \\
You shall be Answered! \\
\end{verse}

\newpage

\poemtitle{Genesis}
\settowidth{\versewidth}{Than Tycho Brahe, or Erra Pater:}
\begin{verse}[\versewidth]
Wordsmith! \\
Yes. \\
I am out of words. \\
You've used them all? \\
I have. \\
You've constructed every combination, \\
Every image, it's inverse, it's complement. \\
No. \\
But you need \textit{new} words? \\
Yes. \\
For what purpose? \\
All the words I have, \\
Have, but only defined an edge. \\
Oh? And beyond that? \\
I cannot see. \\
You have not been? \\
I cannot go. \\
Because... \\
Because I have not the words. \\
Where is it you wish to go? \\
I do not know. \\
Where is it you wish to go? \\
I cannot define! \\
Speak! And it will be. \\
Be? \\
The world you wish it, \\
To be. \\
\end{verse}

\newpage

\definecolor{DeepBlue}{RGB}{0, 0, 99}
\poemtitle{Um Der Deep}
\settowidth{\versewidth}{Than Tycho Brahe, or Erra Pater:}
\begin{verse}[\versewidth]
\textcolor{DeepBlue} {
A deep blue, \\
Somethingness; \\
Begins to spin. \\
Magic. \\
Incantation wills, \\
It. \\
Magic. \\
Spells spill soft, \\
Atoms. \\
Magic. \\
Nothingness from, \\
Somethingness. \\
Magic, No! \\
Chanting from the deep, \\
Ancient. \\
Magic. \\
Do you practice spells? \\
Spells. \\
Do any of \textit{your spells} make, \\
Magic. Spells. \\
Spells. \\
Have you ever raised the dead with \\
One of your spells? \\
Spells. \\
Is it an incantation if you say it \\
Three times? Spells. \\
Incantation becomes spells \\
Birthed by magic within spells, \\
Within spells magic speaks, \\
Magic. \\
Spells. \\
\\
}
\\
\end{verse}

\poemtitle{Spells}
\settowidth{\versewidth}{Than Tycho Brahe, or Erra Pater:}
\begin{verse}[\versewidth]
This conlcudes tihs evneing's Brodacsat. \\
Rterun to yuor hmoes and, \\
Retire your cyrstals. \\
Radios. \\
If you hvae tubes, \\
Siplmy unplug the pwoer. \\
Tihs cnocludes this evenin'gs Brodacast. \\
\end{verse}


\poemtitle{This}
\settowidth{\versewidth}{Than Tycho Brahe, or Erra Pater:}
\begin{verse}[\versewidth]
First words spoken. All, \\
Other words are inflections \\
On, \\
This. \\
Words, Sons and Daughters \\
Of This. \\
This, the first point. \\
The Pointer, Pointed, Point. \\
This begat that, begat there, \\
Begat, \\
Where. We are all children of This. \\
First word spoken––This. \\
That is but a This that is not \\
Here. Where here is–– \\
\textit{That which is close enough to point,} \\
To. \\
\end{verse}

\poemtitle{Green}
\settowidth{\versewidth}{Than Tycho Brahe, or Erra Pater:}
\begin{verse}[\versewidth]
Green, that which all photons \\
Use their energy to point \\
To a color. \\ 
\\
Green, that which all cells \\
Use their energy to point \\
To a sickness. \\ 
\\
Green, that which all emotion \\
Use their energy to point \\
To a jealously. \\
\\
Green, that which all experience \\
Use their energy to point \\
To a freshness. \\
\end{verse}
\newpage

\poemtitle{Swimming}
\settowidth{\versewidth}{Than Tycho Brahe, or Erra Pater:}
\begin{verse}[\versewidth]
I'm swimming \\
In. \\
Your. \\
Eyes. \\
Treading, swimming \\
Words; \\
And I'm just swimming \\
In. \\
Your. \\
Eyes. \\
I can't hear a thing. \\
Over the sounds, \\
From under the waves, \\
Wakes. \\
\textit{Ksshhhhh}\\
I see only seas \\
As far as I can see. \\
I'll just be swimming \\
In. \\
Your. \\
Eyes. \\
\end{verse}

\newpage
\poemtitle{Striped Shirt}
\settowidth{\versewidth}{Than Tycho Brahe, or Erra Pater:}
\begin{verse}[\versewidth]
You and your striped shirt \\
Talking. \\
Jesus Christ, those fucking \\
Stripes \\
So hot, I'll sing \\
Tea kettle. \\
If I'm Chandler Bing, \\
Could you \textit{Be} any hotter? \\
Thinking. \\
Shit, is my fucking mouth open? \\
Tanking. \\
You think it's because Monica and Rachel \\
Wore stripes? \\
I don't. \\
You got that something \\
That I'm just lost in \\
Swimming in, \\
Your, \\
Big. \\
Worldly. \\
Eyes. \\
You and your stripes. \\
\end{verse}

\poemtitle{And Now, Flowers}
\settowidth{\versewidth}{Than Tycho Brahe, or Erra Pater:}
\begin{verse}[\versewidth]
And now \\
It's Flowers \\
Fuh \\
King \\
Flowers. \\
\\
So pretty \\
It's almost \\
Painful. \\
\\
Pink and \\
Yellow petals \\
Green leaves \\
weave \\
\\
Flower patterns \\
So pretty \\
It's almost \\
Painful.
\\
\end{verse}

\poemtitle{Sh(Yeah)}
\settowidth{\versewidth}{Than Tycho Brahe, or Erra Pater:}
\begin{verse}[\versewidth]
You say, \\
``Romantic". \\

I say, \\
Pedantic. \\
\\
I've been called, \\
Casanova \\
Before. \\
\\
I've had \\
Enough heartbreak \\
To know \\
I should \\
Break \\
First \\
Break before it hurts. \\
How romantic, \\
I just feel Baroque. \\
\end{verse}

\newpage
\poemtitle{Beginning}
\settowidth{\versewidth}{Than Tycho Brahe, or Erra Pater:}
\begin{verse}[\versewidth]
Brought to the \\
Edge of reason \\
Among the elements of the \\
Universe, \\
Thoughtless, \\
In my appearance \\
Forever \\
Under \\
Love's Spells. \\
\end{verse}

\poemtitle{Check}
\settowidth{\versewidth}{Than Tycho Brahe, or Erra Pater:}
\begin{verse}[\versewidth]
Testing... \\
One. \\
Two. \\
Three. \\
This concludes this \\
Evening's test. \\
This is not a test. \\
Report to the nearest \\
Check \\
Point \\
This concludes this evening's broadcast. \\
\end{verse}
\newpage
\poemtitle{Feels}
\settowidth{\versewidth}{Than Tycho Brahe, or Erra Pater:}
\begin{verse}[\versewidth]
The way you make me feel \\
Concrete \\
Smooth and rough around the edges \\
Edges \\
You reveal them to me \\
In my dreams \\
In my imagination \\
You make, \\
Me \\
Feel \\
Things \\
Like concrete.
Be a mason \\
Smooth me out \\
Build me up \\
I will support you \\
Like concrete \\
Put rebar in my bones \\
Shades of Grey \\
My favorite thing \\
Like concrete \\
\end{verse}

\poemtitle{Will}
\settowidth{\versewidth}{Than Tycho Brahe, or Erra Pater:}
\begin{verse}[\versewidth]
Will you go somewhere \\
I cannot follow \\
Will you go? \\
\\
Will you go somewhere \\
That's hard to swallow \\
Will you go? \\
\\
Will you go somewhere \\
Without saying goodbye \\
Good–– \\
Bye? \\
\\
Will you go somewhere \\
Without me \\
Don't go. \\
\\
I know you will.
\end{verse}

\newcommand\tab[1][1cm]{\hspace*{#1}}

\poemtitle{Dance}
\settowidth{\versewidth}{Than Tycho Brahe, or Erra Pater:}
\begin{verse}[\versewidth]
May I \\
Have \tab \tab Thought you'd \\
This \tab \tab Never \\
Dance \tab Ask \\
\\
That'd be \\
Nice \tab \tab What took \\
Yeah \tab \tab you \\
\tab \tab so \\
\tab long \\
\\
I \tab \tab \tab Excuses \\
\tab \tab I'd love \\
\tab \tab To \\
\tab \tab Hear \\
\tab \tab Them \\
At \tab \tab The \\
\tab Dance \\
\end{verse}

\poemtitle{A L O N E}
\settowidth{\versewidth}{Than Tycho Brahe, or Erra Pater:}
\begin{verse}[\versewidth]
Learn to be alone \\
\tab be alone \\
\tab be alone \\
\\
Gotta, \\ 
\\
Learn to be alone \\
\tab be alone \\
\tab be alone \\
\\
Learn to be A L O N E. \\
\end{verse}
\newpage
\poemtitle{Where's}
\settowidth{\versewidth}{Than Tycho Brahe, or Erra Pater:}
\begin{verse}[\versewidth]
What's \\
It \\
Like? \\
Living on Planet \textbf{Mars}? \\
\\
Does it feel any different? \\
\\
Looking \\
At \\
The stars? \\
\\
Do you still wander? \\
\\
In \\
Parking \\
Lots? \\
\\
Wondering, ``where did my" \\
C\textbf{ar go}? \\
\end{verse}


\poemtitle{Beach}
\settowidth{\versewidth}{Than Tycho Brahe, or Erra Pater:}
\begin{verse}[\versewidth]
Do you like the beach? \\
Yeah \\
Wanna Go? \\
\textit{\textbf{Yeah}} \\
Wanna meet, there \\
Or \\
My truck, \\
Your truck \\
It'll be cold \\
For who? \\
For us? \\
If we're an us, \\
It won't be \\
So, \\
The beach, \\
The beach, \\
\end{verse}

\newpage
\poemtitle{Click}
\settowidth{\versewidth}{Than Tycho Brahe, or Erra Pater:}
\begin{verse}[\versewidth]
Hey, \\
Yeah. \\
Babe. \\
Yeah... Okay. \\
Come to bed, \\
Okay. \\
\textbf{The lights}. \\
Mmk. \\
The locks? \\
I'll check. \\
Front, back, garage, \\
Stove's off, dogs \\
Asleep. \\
\tab I love when she wears \\
\tab My big baggy sweatshirt \\
\textbf{Click}. \\
\end{verse}

\poemtitle{Treat, Never, Keep, Keep}
\settowidth{\versewidth}{Than Tycho Brahe, or Erra Pater:}
\begin{verse}[\versewidth]
keep your head down \\
and your heart \\
buried \\
\\
make your love, your \\
peace rather, and \\
leave \\
\\
don't stay long \\
you'll only make it \\
worse \\
\\
––hurt em now, hurt em later–– \\
what's the difference \\
? \\
\\
keep your head down \\ 
and you heart \\
hurried \\
\\
keep you heart down \\
and your head \\
typical \\
\end{verse}

\poemtitle{Only Fools Fall}
\settowidth{\versewidth}{Than Tycho Brahe, or Erra Pater:}
\begin{verse}[\versewidth]
I'm a fool. \\
A fool to \\
Fall. \\
\\
Not I \textit{was}, \\
But, I am, \\
A fool \\
\\
Not fell, \\
I'm currently \\
Still \\
Falling \\
\\
Having caught, \\
Myself \tab three \\
Quarters down. \\
\\
{\tab -- \tab } knowing, \\
I'll have to \\
Go all \\
The \\
Way \\. \\
\\
A less-wise man once said, \\
Wise men say \\
``Only fools fall in'' \\
Love. \\
\end{verse}

\newpage

\poemtitle{Wells}
\settowidth{\versewidth}{Than Tycho Brahe, or Erra Pater:}
\begin{verse}[\versewidth]
Well, there it is \\
Almost. \\
\tab It's almost over, \\
\tab \tab But it will be. \\
Not for any other \\
Reason than it was \\
supposed to be\\
\\
You made the right choice \\
Me, I'm \textit{typical}. \\
Who you chose, \\ 
I knew you would. \\
\\
I would've chose \\
The same if it \\
Weren't for you \\
Mind magnetic \\
Heart, \\
Forget it. \\
\\
Wish I could've \\
Put mine in a a \\
Safe–– \\
Ty \\
De - posit box. \\
\\
Nah, Fuck it. \\
Good - Almost - Bye. \\
This is pretty much \\
It. \\

\\
Wasn't anything to begin with. \\
\end{verse}

\poemtitle{Crazing}
\settowidth{\versewidth}{Than Tycho Brahe, or Erra Pater:}
\begin{verse}[\versewidth]
Haven't been this crazy \\
For \\
A \\
Long \tab \tab \tab Time.
\\
Wish our time was \\
A \\
Long \\
\\
\\
Time. \\
\\
Just trying to stretch it \\
\tab \tab out \\
Maybe I'm Just \\
\\
Yeah, maybe. \\
Yeah, maybe I'm \\
Just \\
Crazy \\
, \\
\end{verse}

\poemtitle{Heart}
\settowidth{\versewidth}{Than Tycho Brahe, or Erra Pater:}
\begin{verse}[\versewidth]
Feelings never felt \\
Purely platonic \\
\\
Never this Feeling \\
P  l  a  t  o  n  i  c \\
\\
Happy for you \\
Sad for you \\
Mad for you \\
Patient for you \\
\\
I is no factor \\
\\
Fidelity at your \\
Command \\
\\
Changed me. Rearranged me. \\
Purely, \\
Platonic \\
Absent Humanity \\
But more humane than \\
Just \\
Human \\
\\
Human without excuse \\
Without abuse, \\
Platonic \\
\\
A thousand lives lived \\
And I'm so terribly \\
Happy, \\
I \\
Found \\
You. \\
\end{verse}

\poemtitle{Every New Beginning}
\settowidth{\versewidth}{Than Tycho Brahe, or Erra Pater:}
\begin{verse}[\versewidth]
Last day, \\
Never imagined it'd end \\
This way \\
\\
Last day, \\
Guess we just go our \\
Separate ways \\
\\
Last day, \\
I wouldn't rather it any \\
Other way \\
\\
Last day, \\
And you wouldn't know it \\
Last day, \\
And you aren't finished \\
Changing \\
My \\
Ways. \\
\end{verse}

\poemtitle{The End}
\settowidth{\versewidth}{Than Tycho Brahe, or Erra Pater:}
\begin{verse}[\versewidth]
This marks the end of one period of time. \\
The following words are written after the above \\
Pivotal time. \\
After time. \\
The following are After Sight, \\
After Time. \\
A life lived in \\
Retrospect \\
\end{verse}

\poemtitle{Where The Forest Is}
\settowidth{\versewidth}{Than Tycho Brahe, or Erra Pater:}
\begin{verse}[\versewidth]
Where’s the forest \\
I can see the trees \\
What’s a tree laid bare \\
Without it’s leaves \\
They must not be fingertips \\
But something else \\
Neither tentacle nor \\
Claw, though they may wrap \\
‘Round fallen logs and dig \\
Down till they meet their feet \\
Buried beneath the quiet beast \\
Where the forest is. \\
\end{verse}

\poemtitle{Still Thrills}
\settowidth{\versewidth}{Than Tycho Brahe, or Erra Pater:}
\begin{verse}[\versewidth]
What quiet is \\
Is not distraught \\
That is, what quiet thoughts \\
Talk in the stillness of \\
The thrillness of \\
The realness of \\
Stopped clocks \\
That is, quiet is \\
Quiet is, \\
Quiet is not quite \\
Is, unrequited— \\
That \textit{Is} what quiet is \\
Love, unrequited. \\
\end{verse}

\poemtitle{Bellona}
\settowidth{\versewidth}{Than Tycho Brahe, or Erra Pater:}
\begin{verse}[\versewidth]
She came to me \\
Within a dream, \\
She offered her painted sword; \\
Bellona, I said \\
She came to offer me my \\
Immortality \\
Bell \\
Lon \\
Na. \\
The price, the price was \\
That for everything I create \\
I must destroy another \\
There may never be \\
Two lovers \\
Never be two kingdoms \\
Where I am \\
Is where I must be \\
With both feet, sword, \\
Bellona makes this plea \\
Ezra, reach out and grasp on \\
To your \textbf{immortality} \\
\end{verse}

\poemtitle{Mars En Lieu}
\settowidth{\versewidth}{Than Tycho Brahe, or Erra Pater:}
\begin{verse}[\versewidth]
You are in my \\
Dreams \\
Not my literal dreams \\
Just the day \\
Dreams \\
I force myself \\
To have \\
To keep you in \\
My memory \\
To hold on to \\
The bittersweet \\
\end{verse}

\poemtitle{Good Knights}
\settowidth{\versewidth}{Than Tycho Brahe, or Erra Pater:}
\begin{verse}[\versewidth]
Goodnight is so much easier than \\ 
Goodbye \\
Say it out loud, \\
Good— \\
Bye \\
Say it proud-ly, \\
Good— \\
Bye \\
So final. \\
More final than, \\
Goodnight.\\
A good knight \\
Bids farewell \\
\end{verse}


\poemtitle{Matrimony}
\settowidth{\versewidth}{Than Tycho Brahe, or Erra Pater:}
\begin{verse}[\versewidth]
I turn my headphones up \\
And let the world melt around me \\
As my feet melt into the street \\
\textit{This} is the sound monogamy makes \\
Myself, and my bride; her name is \\
Loneliness \\
\\
Every passerby is here with us at \\
The ceremony and I am grateful for your \\
Attendance \\
\\
Dearly beloved, we are gathered here \\
Today to join together in holy— \\
Matrimony \\
This [pronoun] and this loneliness. \\
\\
Do you [name], take this loneliness to be your Lawfully wedded [pronoun]? \\
\\
I do. \\ 
\\
Do you Loneliness, take this [pronoun] to be \\
Your Lawfully wedded [pronoun]? \\
\\
I already have. And, \\
I will, And, \\
I \\
Do. \\
\end{verse}

\poemtitle{Welling}
\settowidth{\versewidth}{Than Tycho Brahe, or Erra Pater:}
\begin{verse}[\versewidth]
Stepping off the curb \\
As, \\
As the music wells up \\
Through, \\
Through the speakers in my \\
Ears. \\
\\
I could imagine myself Dancing \\
Through, \\
Through the streets and \\
That, \\
That others would join me \\
\\
Arms outstretched, like the \\
Actual sound of music \\
Can you hear it \\
Do you feel it as \\
Kinetically \\
In. \\
Your. \\
Bones. \\
\\
Does it well up beneath your \\
Eyes? \\
Are you overwhelmed by the sheer \\
Beauty \\
Of \\
It \\
All? \\
\end{verse}

\poemtitle{Blink}
\settowidth{\versewidth}{Than Tycho Brahe, or Erra Pater:}
\begin{verse}[\versewidth]
I see you \\
\tab I see you how I wish \\
To \\
See \\
You. \\
\\
You're as much reality as imagination \\
You're an idealization and, \\
A realization. \\
\\
You're a war zone \textit{And} \\
First \\
Aid \\
Station \\
\\
Do you ever think of me? \\
Am I ever in your dreams? \\
Do you cherish moments and \\
Memories, or \\
Do you merely \\
Blink \\
\end{verse}

\poemtitle{Saftey Deposit}
\settowidth{\versewidth}{Than Tycho Brahe, or Erra Pater:}
\begin{verse}[\versewidth]
Will you be my Box? \\
I want a dangerous life and \\
I'd like to keep \\
Some \\
Things \\
Safe. \\
\\
My heart for starters \\
Will you hold on to it \\
And not \\
Mis \\
Place \\
It? \\
\\
As the box begins to weigh \\
Will you waver? \\
Do you love me enough \\
To carry all \\
My \\
Things? \\
\\
Is it enough to only \\
Live with a box \\
Of all \\
My \\
Things? \\
\end{verse}

\poemtitle{Mind Magnetic}
\settowidth{\versewidth}{Than Tycho Brahe, or Erra Pater:}
\begin{verse}[\versewidth]
Your mind, \\
Magnetic. \\
I know about Gravity \\
But our proximity makes \\
Me, \\
Forget it. \\
The way you speak, \\
Aesthetic; \\
Pray you never touch me; \\
Electric–– \\
Shock. \\
Each and every moment with you–– \\
Climatic \\
Your Mind, magnetic \\
Us, We, \textit{Our}? \\
Forget it. \\
\end{verse}

\newpage
\poemtitle{As I Will}
\settowidth{\versewidth}{Than Tycho Brahe, or Erra Pater:}
\begin{verse}[\versewidth]
Asked to accept \\
My immortality. \\
To take my place \\
Among the gods \\
I must refuse \\
Pleasant, to think \\
Such heritage \\
Implies one is unbound \\
I know the owner of \\
My chains \\
As a god, \\
Who would \\
Own; \\
My; \\
Chains; \\
Must I hold them \\
\tab myself? \\
What good is it, then \\
To be god?––none. \\
Prometheus set me \\
Free \\
I have no intention of \\
Enslaving my \\
––Gift, for–– \\
The cheap sum of \\
Eternity \\
\end{verse}

\newpage
\poemtitle{Yield}
\settowidth{\versewidth}{Than Tycho Brahe, or Erra Pater:}
\begin{verse}[\versewidth]
In the midst of chaos \\
I hear the wheels of \\
Your chariot speak \\
Your spear pierces \\
The cloud which chaos \\
Makes. Your helmet \\
Donned, polished and \\
On it, your enemies \\
See their fate in their \\
Own eyes. You lay their \\
Future bare before them. \\
When our paths met, \\
We Battled, I yielded. \\
Sword drawn at my \\
Throat; I could do nothing. \\
But, lose myself in the eyes \\
Behind polished metal \\
You removed your helmet \\
Breathing;––quick, shallow, \\
\\
Breaths \\
\\
You welcomed me \\
Into your immortality \\
Into our eternity \\
\end{verse}

\poemtitle{Metallic}
\settowidth{\versewidth}{Than Tycho Brahe, or Erra Pater:}
\begin{verse}[\versewidth]
Must you always \\
Wear, metal on \\
Your feet \\
\\
Must you always \\
Make, thuds when \\
Your sandals \\
Plant the Earth \\
\\
Breast plate as Beautifully, \\
Fitting \\
What is more important is; \\
What is beneath; Beating; \\
\\
Your beating heart; A heart of \\
Molten Gold. \\
\\
Must you always \\
Make, war and \\ 
Rain destruction and \\
Reign destruction \\
\\
You must, Oh, \\
Bellona. Lay waste as \\
You see fit \\
\\
Yield when your \\
Heart is content \\
When your thirst \\
Has been quenched \\
\end{verse}

\poemtitle{Swinging}
\settowidth{\versewidth}{Than Tycho Brahe, or Erra Pater:}
\begin{verse}[\versewidth]
Speak words to me \\
Let me bathe in your \\
Intonation. \\
\\
Speak words onto me \\
Wrap me in your guard; \\
Say everything \\
\\
Swinging as I'm hanging \\
On, \\
Every. \\
\tab Single. \\
\tab \tab Word. \\
\\
Gleaming, as I hang \\
These moments in my \\
Mind. \\
\\
Memories in frame. \\
\\
Memories spoken into my mind \\
Carried by, \\
The sounds which your \\
Mind–– \\
Makes. \\
\end{verse}

\poemtitle{ReLu}
\settowidth{\versewidth}{Than Tycho Brahe, or Erra Pater:}
\begin{verse}[\versewidth]
Whirlwind, come in \\
Knocked hard with your \\
Huffing; Puffing; Sweating; \\
\\
Why are you always \\
In a hurry? \\
\\
Whirlwind, come in \\
With your flowers \\
With your stripes \\
With your fright \\
\tab your courage \\
With your might \\
\\
Why are you always \\
In a hurry? \\
\\
Whirlwind, come in \\
You need not be quiet here \\
If you want, storm in me \\
Within my shell you may do so, \\
Quietly. \\
\\
I love and hate your \\
Hurrying. \\
\\
Your, \\
Huffing \\
Puffing \\
Sweating \\
\\
Your hurrying. \\
\end{verse}

\newpage
\poemtitle{Right Luck}
\settowidth{\versewidth}{Than Tycho Brahe, or Erra Pater:}
\begin{verse}[\versewidth]
I see you every \\
\tab where \\
\tab \tab I look \\
\\
––Rephrase–– \\
\\
I'm hoping to see you \\
\tab every; where; \\
\tab \tab I look \\
\\
Don't know what I'll do \\
\tab if I do see you \\
\tab \tab probably \\
\tab \tab just \\
\tab \tab cower. \\
\\
You blind my thoughts \\
\tab my mind \\
\tab take my time. \\
\\
And I cross \\
\tab none \\
\tab \tab of \\
\tab \tab \tab yours. \\
\end{verse}


\poemtitle{Reconstituted}
\settowidth{\versewidth}{Than Tycho Brahe, or Erra Pater:}
\begin{verse}[\versewidth]
I am beginning to remember, \\
\\
Remember when, I \\
Formed the world; \\
The \textit{Universe}. \\
\\
Vaguely, \textit{I} remember \\
Taking every piece of \\
Myself \\
And placing it anew \\
\\
Self, Deconstructed \\
Self, We-Becoming \\
Self, Decomposed, in \\
Order to \textit{Compose} \\
All that you \textit{can} see \\
And \\
Every;-thing you \\
Can \\
––Not. \\
\\
My being, became Matter \\
My emotion, became Force \\
Molecularly, one for one \\
Reconstituted \\
\\
I shed every piece of \\
My immortality \\
Accidentally, becoming \\
Human; Being-Becoming \\
Perhaps, Un–– \\
Becoming. \\
\\
Walking on a ba\textit{rr}en \\
Earth, the Crust cried \\
Out \\
\\
``Give to Us!'' \\
\\
Here are my tears; \\
\\
``Seas!'' \\
Here are my feet; \\
\\
``Shores!''
\\
––Dissipating–– \\
\\
``Give to Us!!'' \\
\\
Cloak yourself in my skin–– \\
Atmosphere \\
\\
``GIVE!'' \\
\\
open \\
\\
``Give to Us!'' \\
\\
I. Said. Open! \\
\\
The crusted open Door \\
Revealed an empty Core––\\
\\
``Give!'''
\\
I poured out my \textbf{molten heart} \\
Into the Deep \\
Infatuations decomposed to–– \\
Magnetism \\
Aspirations disposed by–– \\
Rotations \\
\\
Here we are \\
Together, \\
Spinning, Dancing \\
\\
On the edge of our \\
World; Bound \\
Together by \\
This \\
Magmatic \\
Mind. \\
\\
Convoluted, folded \\
Retired to the Deep. \\
\\
I walk among you, \\
A shell of a man \\
An embarrassment to \\
The gods. \\
A crack through–– \\
––Space and time.
\\
And yet, \\
When I plant my \\
––Mortal feet, \\
With each breath, \\
As the wind kisses, \\
My, \\
Cheeks \\
I remember creation \\
\\
––And why I exchanged \\
Immortality for \\
Humanity \\
\end{verse}

\attrib{Ezra (2018)}
\end{document}
 